
\begin{enumerate}
\item Is every polynomial equation solvable by the method of radicals?
\item Equivalently does there exist an explicit "formula" which gives all solutions of an arbitrary polynomial equation?
\end{enumerate}

If the degree of  the polynomial \(f\) is at most four then the answer is "yes".

\section{Formulation of the Classic Problem}
The "formula" by the method of radicals means the formula involving only field operations and the extraction of nth roots. 
The existence of a "formula" means there is a finite sequence of steps, each step being a field operatioin or the extraction of an nth roots, which yields all solutions of the given polynomial. 
Performing a field operatioin leaves the base field unchanged, but the extraction of an nth root of an element 
\(c\) in a field \(K\) amounts to constructing an extenstion field \(K(u)\) with \(u^n \in K\). Thus the existence of a "formula" for solving \(f(x)=0\) would imply 
the existence of a finite tower of fields \\
\[K=E_0 \subset E_1 \subset ... \subset E_n\]
such that \(E_n\) contains a splitting field of \(f\) over \(K\) and for each \(i \geq 1\), \(E_i=E_{i-1}(u_i)\) with some positive power of \(u_i\) lying in \(E_{i-1}\).\\

Conversely suppose there exists such a tower of fields and that \(E_n\) contains a splitting field of \(f\). Then 
\[E_n = K(u_1,u_2,...,u_n)\]
and each solution is of the form \(f(u_1,...,u_n)/g(u_1,...,u_n)\) where \(f,g \in K[x_1,...,x_n]\). \\
Thus each solution is expressible in terms of a finite number of elements of \(K\), a finite number of field operations and \(u_1,...,u_n\). But 
this amounts to saying that there is a "formula" for the solutions of the particular given equation. \\

\begin{definition}[Radical Extension]
An extenstion field \(F\) of a field \(K\) is a radical extenstion of \(K\) if \(F=K(u_1,...,u_n)\), some power of \(u_1\) lies in \(K\) and for each \(i \geq 2\), some power of \(u_i\) lies in \(K(u_1,...,u_{i-1})\).
\end{definition}

\begin{remark}
If \(u_i^m \in K(u_1,...,u_{i-1})\) then \(u_i\) is a root of \(x^m-u_i^m \in K(u_1,...,u_{i-1})[x]\). \\
Therefore every radical extenstion \(F\) of \(K\) is finite dimensional algebraic over \(K\).
\end{remark}

\begin{definition}
The equation \(f(x)=0\) is \textit{solvable by radicals} if there exists a radical extenstion \(F\) of \(K\) and splitting field \(E\) of \(f\) over \(K\) such that \(F \supset E \supset K\).
\end{definition}

\begin{theorem}
If \(F\) is a radical extenstion of \(K\) and \(E\) is an intermediate field, then \(Aut_K^E\) is a solvable group.
\end{theorem}

\begin{corollary}
If the equation \(f(x)=0\) is solvable by radicals, then the Galois group of \(f\) is a solvable group.
\end{corollary}

\section{Group Theoritic Concepts}
Let \(G\) be a group. 

\begin{definition}[Solvable Series]
A finite chain of subgroups \(G=G_0>G_1>...>G_n={e}\) such that \(G_{i+1}\) is normal in \(G_i\) for \(0 \leq i < n\) is called a subnormal series of \(G\).\\
A subnormal series is a solvable series if each factor group \(G_i/G_{i+1}\) is abelian.
\end{definition}

\begin{definition}[Solvable Group]
A group is solvable if and only if it has a solvable series.
\end{definition}

If \(F\) is a radical extension of \(K\) then \(F\) is Galois over \(K\) and by the Fundamental Theorem of Galois \(Aut_K^E\) has a solvable series where \(E\) is an intermediate field. So \(Aut_K^E\) is solvable.

\section{Conclusion}
\begin{theorem}
The symmetric group \(S_n\) is not solvable for \(n \geq 5\).
\end{theorem}

The polynomial \(f(x)=x^5-4x+2 \in \mathbb{Q}[x]\) has Galois group \(S_5\), which is not a solvable group. \\ \\
The quantic polynomials over \(\mathbb{Q}\) are not solvable by radicals. That is there does not exist an explicit formula for solving the quantics. \\
Moreover, polynomials of degree \(n \geq 5\) are not solvable by radicals.

\begin{remark}
The base field plays an important role here. The polynomial \(x^5-4x+2\) is not solvable by radicals over \(\mathbb{Q}\), but it is solvable by radicals over \(\mathbb{R}\) of real numbers. In fact, every polynomial equation over \(\mathbb{R}\) is solvable by radicals since all the solutions lie in the algebraic closure \(\mathbb{C}\) which is a radical extension of \(\mathbb{R}\).
\end{remark}

